Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-16 cav2017/cav2017.tex
cav

% first the title is needed
\title{Automated Synthesis of State-Space Digital Systems}

@@

@@

%-------------------------------
\subsection{State-space representation of dynamical systems}
\label{ssec:ssrepresentation}
%-------------------------------

@@

%-------------------------------
\subsection{State feedback control}
\label{ssec:statefeedbackcontrol}
%-------------------------------

@@

@@

%-------------------------------
\section{Related Work}
%-------------------------------

>>>>

% first the title is needed
\title{Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants}

@@

%-------------------------------
\subsection{Related Work}
\label{sec:relw}
%-------------------------------

\todo{[Move material from \ref{sec:rw} here]}

@@

%-------------------------------
\subsection{State-space representation of physical systems} 
\label{ssec:ssrepresentation}
%-------------------------------

@@

%-------------------------------
\subsection{Controller synthesis via state feedback}
\label{ssec:statefeedbackcontrol}
%-------------------------------

@@

%-------------------------------
\subsection{Digital implementation of feedback controller}
\label{ssec:statefeedbackcontrol}
%-------------------------------

@@

%-------------------------------
\section{Related Work}
\label{sec:rw}
%-------------------------------
